\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2018-06-22 redaction/dhp_july2017.tex
changement tex

\begin{table}[htbp]
  \centering
  \caption{Robustness to the separability assumption}
\begin{center}
    \begin{tabular}{lcccc}
    \hline \hline
    \multicolumn{5}{c}{Mean value over 1974-2013} \\
 \multicolumn{5}{c}{3 digits} \\    \hline \hline
   Mode  & \multicolumn{2}{c}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
    Additive term ($t/\widetilde{p}$. in \%) &       &       &       &  \\
    Mean  & \multicolumn{1}{c}{1.76} & \multicolumn{1}{c}{1.96} & \multicolumn{1}{c}{2.61} & \multicolumn{1}{c}{2.99} \\
    Median & \multicolumn{1}{c}{0.65} & \multicolumn{1}{c}{0.84} & \multicolumn{1}{c}{1.83} & \multicolumn{1}{c}{2.23} \\
    Ad-valorem term (\$\textbackslash{}tau\$. in \textbackslash{}\%) & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    Mean  & \multicolumn{1}{c}{1.04} & \multicolumn{1}{c}{0.94} & \multicolumn{1}{c}{2.43} & \multicolumn{1}{c}{2.40} \\
    Median & \multicolumn{1}{c}{0.56} & \multicolumn{1}{c}{0.83} & \multicolumn{1}{c}{2.06} & \multicolumn{1}{c}{2.04} \\
    Diagnostic tests & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    $R^2$    & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.68} & \multicolumn{1}{c}{0.67} & \multicolumn{1}{c}{0.45} \\
    SER   & \multicolumn{1}{c}{0.57} & \multicolumn{1}{c}{0.72} & \multicolumn{1}{c}{0.53} & \multicolumn{1}{c}{0.69} \\
    AIC criteria & \multicolumn{1}{c}{4657.60} & \multicolumn{1}{c}{4654.23} & \multicolumn{1}{c}{10744.83} & \multicolumn{1}{c}{10690.80} \\
    Log-likelihood & \multicolumn{1}{c}{-1757.75} & \multicolumn{1}{c}{-2258.24} & \multicolumn{1}{c}{-4018.51} & \multicolumn{1}{c}{-5220.00} \\ \hline
\# observations & \multicolumn{1}{c}{2381} & \multicolumn{1}{c}{2381} & \multicolumn{1}{c}{2798} & \multicolumn{1}{c}{2798} \\
\# origin country & \multicolumn{1}{c}{13.4} & \multicolumn{1}{c}{13.4} & \multicolumn{1}{c}{19.8} & \multicolumn{1}{c}{19.8} \\
\# products & \multicolumn{1}{c}{25.5} & \multicolumn{1}{c}{25.5} & \multicolumn{1}{c}{53} & \multicolumn{1}{c}{53} 
    \end{tabular}%
\end{center}
\label{tab:robustness_separability}
\end{table}

>>>>

\begin{table}[htbp]
  \centering
  \caption{Robustness to the separability assumption}
\begin{center}
    \begin{tabular}{lcc|cc}
    \hline \hline
    \multicolumn{5}{c}{Mean value over 1974-2013} \\
 \multicolumn{5}{c}{3 digits} \\    \hline \hline
   Mode  & \multicolumn{2}{c}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
   Separability & No & Yes & No & Yes \\
    Additive term ($t/\widetilde{p}$. in \%) &       &       &       &  \\
    Mean  & \multicolumn{1}{c}{1.76} & \multicolumn{1}{c}{1.96} & \multicolumn{1}{c}{2.61} & \multicolumn{1}{c}{2.99} \\
    Median & \multicolumn{1}{c}{0.65} & \multicolumn{1}{c}{0.84} & \multicolumn{1}{c}{1.83} & \multicolumn{1}{c}{2.23} \\
    Ad-valorem term (\$\textbackslash{}tau\$. in \textbackslash{}\%) & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    Mean  & \multicolumn{1}{c}{1.04} & \multicolumn{1}{c}{0.94} & \multicolumn{1}{c}{2.43} & \multicolumn{1}{c}{2.40} \\
    Median & \multicolumn{1}{c}{0.56} & \multicolumn{1}{c}{0.83} & \multicolumn{1}{c}{2.06} & \multicolumn{1}{c}{2.04} \\
    Diagnostic tests & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    $R^2$    & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.68} & \multicolumn{1}{c}{0.67} & \multicolumn{1}{c}{0.45} \\
    SER   & \multicolumn{1}{c}{0.57} & \multicolumn{1}{c}{0.72} & \multicolumn{1}{c}{0.53} & \multicolumn{1}{c}{0.69} \\
    AIC criteria & \multicolumn{1}{c}{4657.60} & \multicolumn{1}{c}{4654.23} & \multicolumn{1}{c}{10744.83} & \multicolumn{1}{c}{10690.80} \\
    Log-likelihood & \multicolumn{1}{c}{-1757.75} & \multicolumn{1}{c}{-2258.24} & \multicolumn{1}{c}{-4018.51} & \multicolumn{1}{c}{-5220.00} \\ \hline
\# observations & \multicolumn{1}{c}{2381} & \multicolumn{1}{c}{2381} & \multicolumn{1}{c}{2798} & \multicolumn{1}{c}{2798} \\
\# origin country & \multicolumn{1}{c}{13.4} & \multicolumn{1}{c}{13.4} & \multicolumn{1}{c}{19.8} & \multicolumn{1}{c}{19.8} \\
\# products & \multicolumn{1}{c}{25.5} & \multicolumn{1}{c}{25.5} & \multicolumn{1}{c}{53} & \multicolumn{1}{c}{53}
    \end{tabular}%
\end{center}
\label{tab:robustness_separability}
\end{table}
